An Imaging Search for Post-MS Companions of Sirius B

### 2021-11-03 paper/paper.tex
update paper with new intro and discussion

\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{cleveref}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{makecell}

@@

%% Define new commands here
\newcommand\latex{La\TeX}

@@

\title{An Imaging Search for Circumstellar Companions of Sirius B}

\shorttitle{An Imaging Search for Circumstellar Companions of Sirius B}
\shortauthors{Lucas et al.}

@@

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities and sub-AU separations, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au} down to a sensitivity of \qty{0.6}{\jupitermass} at \qty{1.5}{\au}. The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the precisely known Sirius B system age. Consistent with previous results, we do not detect any companions around Sirius B.
\end{abstract}

@@

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Probing the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. Imaging a planet is challenging, however. The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet. In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.

White dwarfs (WD) are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their main-sequence (MS) progenitors which reduces the contrast necessary to detect a companion. In addition, the relative lack of spectral features of WDs makes them imprecise targets for radial velocity analysis. The intrinsic faintness of WDs proves challenging for all detection methods; this is exacerbated on ground-based telescopes which require significant signal-to-noise (S/N) to operate their adaptive optics (AO) facilities. This implicitly limits searches of WDs to the $\sim$\qty{100}{\parsec} neighborhood. Little is known about post-MS planetary evolution, however, planets that are tenuous enough to survive the red giant and asymptotic giant phases of its host are interesting laboratories for planetary formation pathways as showcased by recent discoveries like giant planet candidate WD 1856+534b \citep{vanderburgGiantPlanetCandidate2020}.

In this work, we briefly review post-MS planetary formation theory (\cref{sec:post-ms}) and discuss the Sirius system, specifically bright WD Sirius B, as potential exoplanet hosts (\cref{sec:sirius}). In \cref{sec:obs}, \cref{sec:analysis}, and \cref{sec:results} we describe our observations of Sirius B in 2020, along with the subsequent analysis. Finally, in \cref{sec:conclusion} we discuss the implications of our observations for planetary formation theory and future work.

\section{Post-MS Evolution} \label{sec:post-ms}

There is limited knowledge of planetary systems around evolved stars. \citet{burleighImagingPlanetsNearby2002a,verasPostmainsequencePlanetarySystem2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase. Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}. During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeansCosmogonicProblemsAssociated1924}. In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.

The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}. \citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf. \citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

\section{Sirius B and the Sirius System} \label{sec:sirius}

A particularly fascinating target is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

A common problem in direct imaging is determining planetary masses from photometry using planetary atmosphere evolution grids. This method of interpolation depends on the stellar age, the stellar photometry, and the distance to the system. Determining stellar ages is quite difficult and sometimes impossible, and is often the largest source of uncertainty when interpolating planetary masses. Age uncertainty exponentially affects young systems (\textless\qty{1}{\giga\year}) due to the rapid cooling of giant planets. Sirius B avoids these pitfalls due to its unusually high age precision, primarily derived from accurate dynamical masses.

The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{besselVariationsProperMotions1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bondCompanionSiriusProf1862} as Sirius B. \citet{adamsSpectrumCompanionSirius1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. \citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories. \citet{bondSiriusSystemIts2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

To find the total age of Sirius B, \citet{bondSiriusSystemIts2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first. Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummingsTwoMassiveWhite2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bondSiriusSystemIts2017}. An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.

The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}). \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathakHighContrastImaging2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

In this work, we report direct images of Sirius B with Keck/NIRC2. The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.

\section{Observations} \label{sec:obs}
\defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
\defcitealias{bondSiriusSystemIts2017}{B17}
\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
\defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
\begin{deluxetable}{cccc}
    \tablecaption{Parameters of the Sirius system adopted in this study.\label{tbl:system}}
    \tablehead{
        \colhead{parameter} & \colhead{value} & \colhead{unit} & \colhead{ref.}
    }
    \startdata
    $t_\mathrm{sys}$ & 226 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $\pi$ & \num{374.5\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
    $d$ & \num{2.67\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
    \cutinhead{Sirius A}
    $M_\star$ & \num{2.063\pm0.023} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius B}
    $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    $t_\mathrm{WD}$ & 125 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018}\\
    $m^{Lp}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
    $M^{Lp}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
    \enddata
\end{deluxetable}

\begin{deluxetable*}{ccccccccc}[t]
    \tabletypesize{\small}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
    \label{tbl:obs}}
    \tablehead{
        \colhead{\makecell{Date\\observed}} &
        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
        \colhead{\makecell{Obs.\\time} (hr)} &
        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
        \colhead{FWHM (\unit{\milliarcsecond})} &
        \colhead{Seeing (\unit{\arcsecond})} &
        \colhead{Temp (\unit{\celsius})} &
        \colhead{PWV (\unit{\milli\meter})}
    }
    \startdata
    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.8 & 3.5 \\
    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
    \enddata
\end{deluxetable*}

% \begin{deluxetable}{ccccc}
%     \tabletypesize{\small}
%     \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}). Observation time is based on the frames that were selected for processing. Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
%     \label{tbl:obs}}
%     \tablehead{
%         \colhead{Epoch} &
%         \colhead{2020-02-4} &
%         \colhead{2020-11-21} &
%         \colhead{2020-11-28} &
%         \colhead{}
%     }
%     \startdata
%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
%     \enddata
% \end{deluxetable}

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{spike}
    \caption{A diffraction spike sweeping across a calibrated science frame of Sirius B from the first epoch. This shows the strong scattered light effects of Sirius A and how they affect the FOV of Sirius B \ang{;;11} away.}
    \label{fig:spike}
\end{figure}

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{psf}
    \caption{The median frame from the second epoch showing the instrumental PSF. The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}. The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
    \label{fig:psf}
\end{figure}

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{cleveref}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{makecell}

@@

%% Define new commands here
\newcommand\latex{La\TeX}
\newcommand\Lp{$\mathrm{L}^\prime$}

@@

\title{An Imaging Search for Post-MS Companions of Sirius B}

\shorttitle{An Imaging Search for Post-MS Companions of Sirius B}
\shortauthors{Lucas et al.}

@@

\begin{abstract}
Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution. We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-MS planetary evolution in the Sirius system. We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging. Our observations are contrast limited out to \qty{1}{\au} and background limited beyond. The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.3} absolute magnitude. We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids. We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.7}{3}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.5}{\jupitermass} at \textgreater\qty{1}{\au}. Consistent with previous results, we do not detect any companions around Sirius B. Our excellent detection limits, even without coronagraphy, demonstrate the capabilities for modern high-contrast imaging studies of nearby (\textless\qty{25}{\parsec}) white dwarfs.
\end{abstract}

@@

\begin{itemize}
    \item add Debes text
    \item run through python scripts/grammarly
    \item reorganize Zenodo sections
    \item remove extra references
    \item compile latex diff
    \item add comments to latex diff referencing referee report
\end{itemize}

In recent decades astronomers have discovered thousands of exoplanets orbiting stars that will eventually evolve into giants and then white dwarfs \citep{akesonNASAExoplanetArchive2013}. The fate of planets around these stars beyond the main-sequence (MS) is uncertain due to the large expansion, stellar winds, and high irradiation encountered on the giant branch \citep{verasPostmainsequencePlanetarySystem2016}. Despite this, direct evidence from white dwarf (WD) pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought. Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.

The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs. As the MS star runs out of Hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius. When Helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation. Eventually the star will run out of fuel and conclude its nuclear burning and become a WD. The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.

There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}. Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}. The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.

Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions. \citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where in multi-star systems the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system). Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with ``hot-start'' planetary formation timescales \citep{spiegelSpectralPhotometricDiagnostics2012a}. A first-generation planet could act as a seed for planetesimal growth in these disks, too. Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies. \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI). \citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted 3-body problem and concluded up to $\sim$10\% of all WD binaries might contain ``star-hopper'' planets which migrate between the stars.

\textbf{John Debes work from 2000-2010 with Spitzer, HST}

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade. In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}). We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).

\section{Directly imaging post-MS systems} \label{sec:imaging}

High-contrast imaging is a powerful technique for discovering and characterizing exoplanets. Directly imaging a circumstellar companion is difficult, though. The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}. In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources. Thermal emission from exoplanets peaks, well into in the infrared, on the Rayleigh-Jeans limit of the stellar spectrum. This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.

WDs are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their MS progenitors which reduces the contrast necessary to detect a companion. The high effective temperatures of WD photospheres pushes the peak thermal emission even further into the optical and ultraviolet, reducing the intrinsic contrast between the star and the planet. In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique. The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby WDs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.

% \section{Post-MS evolution} \label{sec:post-ms}

% There is limited knowledge of planetary systems around evolved stars. The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain. The expansion of the stellar photosphere will engulf companions and cause tidal interactions, destroying planets or disrupting their orbits \citep{burleighImagingPlanetsNearby2002a, nordhausOrbitsLowmassCompanions2013}. Planets that escape engulfment will encounter stellar winds and strong irradiation, causing orbital expansion \citep{jeansCosmogonicProblemsAssociated1924}, enriching the circumstellar environment with metals and dust, and strongly heating planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.

% The observational evidence for planets in post-MS systems is varied. WD atmospheres quickly separate heavy elements in their atmospheres due to their high surface gravity \citep{schatzmanTheorieDebitEnergie1945}, which causes the elements to sink and stratify. The time scale for this phenomena can be days to $\sim$\qty{1}{\mega\year}, significantly shorter than WD cooling ages, which means that most WD atmospheres are comprised of hydrogen, helium, and some carbon. However, metals heavier than carbon have been detected in WDs with cooling ages between \qtyrange{30}{500}{\mega\year}. A common explanation for the ``pollution'' of these WDs is the accretion of planetary material. This is backed up by the evidence of WD debris disks, although only a fraction of all polluted WDs are host to a disk \citep{koesterFrequencyPlanetaryDebris2014}. Chemical analysis shows the pollution is closer to planetary in origin rather than the interstellar medium. Most damning, though, is the correlation between the relative population of polluted WDs (25\% - 50\%) and the expected number of MS planet hosts \citep{koesterFrequencyPlanetaryDebris2014}.

% suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase. Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}. During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet . In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.

% The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}. They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet. They studied $\sim$100 white dwarfs but found no companions. The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38. The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}. It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}. \citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.

% Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf. \citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

\section{Sirius B and the Sirius system} \label{sec:sirius}

One fascinating target for post-MS observations is Sirius B, the closest and brightest WD to our solar system. The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for direct imaging. Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.

Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment. Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}. \citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories. \citet{bondSiriusSystemIts2017} used \textit{Hubble Space Telescope} (HST) data to compile the most precise orbital solution, to date, for Sirius. The dynamical masses were derived using this orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively. A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}. \citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.

The total age of Sirius B is the combination of its WD cooling age and the time from the zero-age MS (ZAMS) to the tip of the giant branch (TGB). We adapt the cooling age derived by \citet[sec. 8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}. We use the updated WD initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.

We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}. These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model. The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}. An age uncertainty of $\sim$4\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all. These values are compiled in \Cref{tbl:system}.

One of the peculiarities of the Sirius system is its large eccentricity of 0.59 \citep{bondSiriusSystemIts2017}. If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
\begin{equation}
    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
\end{equation}
where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states. The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}. If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution. In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}. \citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}. This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage. Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.

\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping'', but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which we would expect to increase with mass transfer to conserve total angular momentum in the binary. \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}. \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components. We extrapolate their Figure 7 using the parameters for Sirius to estimate a $\sim$70\% collision probability for an initial companion of Sirius B if it is chaotically ejected. When combined, these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.

We also consider adiabatic orbit expansion of a substellar companion
\begin{equation}
a_i = a_f \frac{M_{f}}{M_{i}}
\end{equation}
where $a$ is the semi-major axis, and $M$ is the stellar mass of Sirius B. Using the maximum stellar radius of \qty{5.104\pm0.075}{\au} and assuming an extra 20\% separation to escape tidal shredding \citep{nordhausOrbitsLowmassCompanions2013} would create a forbidden region within \qty{31\pm6}{\au} around present Sirius B. In combination with the dynamical stability limits of \qty{1.5}{\au}, we can readily rule out the plausibility of detecting a first-generation companion of Sirius B.
